Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-28 cbm-rbd-paper.tex
other comments by SDF addressed

***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?

@@

@@

>>>>

***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?
common cause failures currently not in the model, but will seriously influence residual life distribution,
see comments in Outlook (Section~\ref{sec:outlook})

@@

***illustrative figure?

@@

***common-cause failures will seriously reduce RLD in a way currently not covered by our model.
This needs to be implemented on the level of component models,
specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
(not a product anymore if common-case failures can affect several component times at once).
Combine ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a}.
